---
title: "case study"
author: "Tianqi Li"
date: "2024-10-08"
output: html_document
---

```{r}
library(tidyverse)
library(leaflet)
```


```{r}
library(p8105.datasets)

data(nyc_airbnb)
```

## Brainstorn questions

* Where are max and min air bnb prices?
  * what are average prices?
  * what factors affect prices?
* Where are prices going up and down over time?
* What is the relationship between number of reviews and average review?
* Does room type affect availability?
* What is the location of the unit?
  * What areas are popular?
  * Popularity = number of units? average price?
* Are there repeat hosts?
  * If so, what does that mean?

```{r}
nyc_airbnb |>
  count(room_type)

nyc_airbnb |>
  count(neighbourhood_group)
```

```{r}
mean(pull(nyc_airbnb,price))
max(pull(nyc_airbnb,price))
min(pull(nyc_airbnb,price))
```

```{r}
nyc_airbnb |>
  group_by(room_type) |>
  summarize(mean_price = mean(price))|>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

```

```{r}
nyc_airbnb |>
  ggplot(aes(x = review_scores_location, y = price)) + geom_point()
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", price < 1000) |>
  ggplot(aes(x = lat, y = long, color = price)) + geom_point(alpha = .1)
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", price < 1000, room_type == "Entire home/apt") |>
  group_by(neighbourhood) |>
  summarize(mean_price = mean(price)) |>
  arrange(desc(mean_price))
  
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", price < 1000, room_type == "Entire home/apt") |>
  mutate(neighbourhood=fct_reorder(neighbourhood,price)) |>
  ggplot(aes(x = neighbourhood, y = price)) + geom_violin() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", price < 1000) |>
  slice(1:10) |>
  leaflet() |>
  addTiles() |>
  addMarkers(~lat, ~long)
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan", price < 1000) |>
  leaflet() |>
  addTiles() |>
  addCircleMarkers(~lat, ~long, radius = 2)
```

```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2)

pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$stars)

nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan", price < 1000) |>
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = 2, color = ~pal(stars))
```

